% LaTeX file for resume

\documentclass[11pt, a4paper]{article}

\usepackage[top=3.75cm, bottom=3.75cm, left=3.75cm, right=3.75cm]{geometry}
\usepackage{hyperref}
\usepackage{adjustbox}
\usepackage{multicol}
\usepackage{fontspec}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{parskip}
\usepackage{microtype}
\usepackage{needspace}

\setlength{\emergencystretch}{5em}
\setlength{\parskip}{10pt plus 2pt minus 1pt}
\hbadness=10000

\hyphenpenalty=10000
\exhyphenpenalty=10000

\setmainfont{Ubuntu}

% Colours
\definecolor{accent}{HTML}{2b2b2b}

% Hyperlink style
\hypersetup{colorlinks=true, urlcolor={blue!60!black}, linkcolor={blue!60!black}}

% Section formatting: small caps, extra space above, no rule
\titleformat{\section}{\large\color{accent}}{}{0em}{}
\titlespacing*{\section}{0pt}{28pt}{10pt}

% Page numbers
\pagestyle{plain}

% Tight lists
\setlist{nosep, leftmargin=0pt, label={}}

\setlength\columnsep{6pt}



\begin{document}

% ---- Header ----
\begin{center}
  {\LARGE\bfseries Thomas Hazell}\\[6pt]
  Somerville College, Woodstock Road, Oxford OX2 6HD\\[2pt]
  \url{thomas.hazell@politics.ox.ac.uk} \enspace$\cdot$\enspace \url{https://t-hazell.github.io/}
\end{center}

\vspace{8pt}

% ---- Research Interests ----
\section{Research Interests}
\vspace*{0pt}
\begin{multicols}{2}
  Autocracy\\
  Bureaucracy \& bureaucrats\\
  Computational social science\\
  Central Asia\\
  Procurement \& corruption\\
  Subnational governance
\end{multicols}

\section{Education}

\begin{samepage}
  \textbf{DPhil (PhD) in Politics} \hfill 2024 -- \phantom{2027}\\
  \textit{Department of Politics and International Relations, University of Oxford}

Funded by an Economic and Social Research Council Studentship. Supervised by Dr Katerina Tertytchnaya.
\end{samepage}

\begin{samepage}
  \textbf{Visiting Graduate Student} \hfill March -- April 2026\\
  \textit{Department of Political Science and International Relations, Nazarbayev University, Astana}
\end{samepage}

\begin{samepage}
  \textbf{MPhil in Politics (Comparative Government)} \hfill 2022 -- 2024\\
  \textit{Department of Politics and International Relations, University of Oxford}

Grade: \textit{Distinction}. Funded by an Economic and Social Research Council Studentship. Thesis: `Subnational governance, patronage, and political careers in Kazakhstan,' supervised by Dr Katerina Tertytchnaya.
\end{samepage}

\begin{samepage}
  \textbf{BA in Philosophy, Politics, and Economics} \hfill 2019 -- 2022\\
  \textit{Lincoln College, University of Oxford}

Grade: \textit{First Class}. Finals examinations in politics and economics. Thesis: `Changing the rules of autocracy: the politics of electoral reform in competitive authoritarian Ukraine,' supervised by Dr Jody LaPorte.
\end{samepage}

\section{Work-in-Progress}

\textbf{Thesis papers}

\begin{samepage}
`Personnel appointments in authoritarian bureaucracies'.

Biased hiring by unelected managers undermines state capacity. Recent work focuses on who gets hired, not the conditions under which it takes place. I argue that, under weak rule of law, bureaucratic managers balance the potential rewards of hiring aligned subordinates with the risk of punishment for breaching civil service regulations. The paper employs novel data on about 7,000 district bureaucrat appointments in Kazakhstan, computationally extracted from over three million administrative records. Combined with hand collected data on manager tenure and detailed administrative statistics, I use two-way fixed effects designs to show that new managers quickly replace subordinates despite civil service regulations, that appointments decline after the departure of their boss, and that there are no equivalent effects for junior staff. The findings highlight how informal politics sustain biased hiring despite civil service reforms.
\end{samepage}

\begin{samepage}
`Social connections and the quality of public procurement'.

How do appointment practices affect governance? A growing literature debates the conditions under which discretionary appointments have negative or, less commonly, positive effects on governance, predominantly drawing on evidence from electoral democracies. It is not yet clear whether these findings extend to authoritarian settings, where the threat of political punishment is greater and bureaucrats' incentives strongly differ. I present new theory on the role of connections in authoritarian bureaucracies, and use novel data from Kazakhstan to test whether bureaucrats' dependence on their civil service managers influences economic outcome. I use new measures of bureaucratic effort, effectiveness, and corruption risk based on six million public procurement processes alongside text-as-data methods on technical specifications to provide direct evidence on bureaucrats' behaviour. The paper provides large-scale bureaucrat-level evidence on the roles of informal connections and personnel politics in shaping state outcomes.
\end{samepage}

\begin{samepage}
`Which merits matter? Political performance, economic meritocracy, and elite loyalty in authoritarian states'.

Which merits do autocrats care about when selecting officials? Some regimes prioritise economic competence and promote based on growth or unemployment figures. Others view political stability as more important. These effects may be conditional or---in many cases---performance may simply not matter for appointments. Work on autocratic meritocracy, nonetheless, should consider wider operationalisation of political merit, provide stronger evidence of merit not mattering, and study cases beyond China and Russia. I advance the literature using newly collected evidence on governors' career trajectories in Kazakhstan paired with economic, electoral, and protest data. I use an equivalence testing approach to provide strong evidence that economic merit—even exceptionally good performance—does not matter in this case, while good political performance can somewhat increase a governors' prospects of promotion. I contribute to work on promotion tournaments and performance incentives under autocracy, while presenting new data from an important but understudied case of hegemonic electoral autocracy.
\end{samepage}

\textbf{Other work}

`Local elections and elite management in authoritarian regimes: evidence from Kazakhstan'. With Eleonora Minaeva and Kirill Melnikov.

`The governance effects of local elections in autocracies'. With Eleonora Minaeva and Kirill Melnikov.

`Shuffling to co-opt: Subnational governance, co-optation, and political careers in Kazakhstan'.

\section{Invited Talks}

`Personnel appointments in authoritarian bureaucracies.' 20 March 2026. Department of Political Science and International Relations, Nazarbayev University, Astana.

\section{Conferences \& Workshops}

`Which merits matter? Political performance, economic meritocracy, and elite loyalty in authoritarian states.' \textit{Conference of the European Political Science Association (EPSA)}. 27 June 2025. UC3M, Madrid.

`Personnel appointments in authoritarian bureaucracies.' \textit{3rd APSG Conference on Authoritarian Politics}. 23 June 2025. Authoritarian Political Systems Group, King's College London.

`Personnel appointments in authoritarian bureaucracies.' \textit{3rd Conference ``New Advances in the Political Economy of Development in Eurasia.''} 6 June 2025. Almaty Management University, Almaty.

`Shuffling to co-opt: Subnational governance, patronage, and political careers in Kazakhstan.' \textit{Conference of the Midwestern Political Science Association (MPSA)}. 5 April 2025. Chicago.

`Shuffling to co-opt: Subnational governance, patronage, and political careers in Kazakhstan.' \textit{ESRC Grand Union DTP Annual Conference}. 4 June 2024. University of Oxford, Oxford.

`Shuffling to co-opt: Subnational governance, patronage, and political careers in Kazakhstan.' \textit{Emerging Scholars Workshop on the Study of Challenges in Eurasian Politics and Society}. 24 May 2024. Center for Slavic, Eurasian, and East European Studies, University of North Carolina at Chapel Hill. Presented Online.

\section{Teaching}

\textit{Undergraduate Tutor}, University of Oxford (sole instructor for weekly one-to-one/small-group teaching)

Comparative Government (Final exams core paper). TT (Summer) 2026.

Politics in Russia and the Former Soviet Union (Final exams options paper). MT (Autumn) 2025, TT (Summer) 2026.

\section{Professional \& Research Experience}

\begin{samepage}
  \textbf{Research Assistant on Non-Violent Repression in Electoral Autocracies}\hfill{}\linebreak September 2024 -- present\\
  \textit{Department of Politics and International Relations, University of Oxford}

Research assistance to Dr Katerina Tertytchnaya's ESRC-funded project on administrative and bureaucratic repression. Including text-as-data/classification, survey data, and event data tasks.
\end{samepage}

\begin{samepage}
  \textbf{Election Observer (Short-term), Uzbekistan} \hfill October 2024\\
  \textit{OSCE ODIHR Election Observation Mission}

UK-seconded short-term observer for the OSCE ODIHR mission in Samarqand region during the 2024 parliamentary elections.
\end{samepage}

\begin{samepage}
  \textbf{Consultant Researcher} \hfill June -- October 2024\\
  \textit{Ridgeway Information, London}

Consultancy supporting the International Atomic Energy Agency (IAEA)'s nuclear non-proliferation work. Open source methods and Russian-language support, especially on projects related to the former Soviet Union.
\end{samepage}

\begin{samepage}
  \textbf{Research Assistant on AUTHLIB (PI: Stephen Whitefield)} \hfill September 2023 -- January 2024\\
  \textit{Department of Politics and International Relations, University of Oxford}

Part of the joint UKRI/Horizon Europe funded project `neo-authoritarianisms in Europe and the liberal democratic response' (\url{https://www.authlib.eu/}), led at Oxford by Stephen Whitefield, Spyros Kosmidis, and Zofia Stemplowska. Coding tweets to train a natural language processing model.
\end{samepage}

\begin{samepage}
  \textbf{Research Assistant to Dr Lenka Buštíková} \hfill May -- September 2023\\
  \textit{Oxford School of Global and Area Studies, University of Oxford}

Data collection for projects on illiberalism and irregular armed groups' political role in Ukraine.
\end{samepage}

\begin{samepage}
  \textbf{Research Assistant on the Oxford University Economic Recovery Project} \hfill February -- Nov 2021\\
  \textit{Smith School of Energy and Enterprise, University of Oxford}

Research assistance, using government and media sources to track state spending in response to Covid-19.
\end{samepage}

\begin{samepage}
  \textbf{Intern} \hfill Summer 2021\\
  \textit{Oxford Internet Institute, University of Oxford}
\end{samepage}

\section{Service}

Reviewer for \textit{Journal of Elections, Public Opinion and Parties} and \textit{Communist and Post-Communist Studies}.

\section{Selected Scholarships \& Awards}

\begin{samepage}
\textbf{Grand Union Doctoral Training Programme Studentship}, Economic and Social Research Council, 2022--2026.

Competitively awarded doctoral studentship, covering fees and stipend for the MPhil in Politics followed by the DPhil (PhD) in Politics, both at Oxford. Value: $\approx$ \pounds 145,000.
\end{samepage}

%\textbf{Language Training Grant}, Department of Politics and International Relations, University of Oxford, 2023--2024.
%
%Funding for a year of Russian courses at the Oxford University Language Centre. Value: \pounds 360.
%
% \begin{samepage}
% \textbf{Research Training Support Grant}, Grand Union Doctoral Training Programme, Summer 2023.

% Grant covering six weeks of intensive Russian language training in Bishkek, Kyrgyzstan. Value: \pounds 820.
% \end{samepage}

\begin{samepage}
\textbf{Tatham Exhibition and College Scholarship}, Lincoln College, University of Oxford, 2020--2022.

Awarded for academic performance. Value: \pounds 450.
\end{samepage}

\section{Languages}

English (Native). Russian (Intermediate). Qazaq (Beginner).

\section{Computer Skills}

\textbf{R} (Advanced): Modelling \& causal inference methods. Survey data. Visualisation. Managing large datasets. Web scraping/automation. Quarto. Machine learning (\texttt{tidymodels}). GIS (\texttt{sf}).

\textbf{Python}: Scraping. Data management. Natural language processing/\allowbreak text-as-data/\allowbreak machine learning, including \texttt{torch}. GIS.

\textbf{\textit{Other}}: OpenAI APIs (Batch, Fine Tuning). Git/GitHub. Cloud computing (Azure, Google Cloud). Databases/\allowbreak basic SQL. \LaTeX.

\section{Additional Training}

\textbf{Qazaq language}, Faculty of Asian and Middle Eastern Studies, University of Oxford, November 2025--.

\textbf{Comprehensive E-learning Course for OSCE/ODIHR Observers}, September 2024.

\textbf{Fieldwork Safety Overseas}, University of Oxford Safety Office, June 2023.

\textbf{Advanced R for the Social Sciences}, Social Sciences Division, University of Oxford, February 2023.

\section{International Experience}

Intensive Russian language training in Bishkek, Kyrgyzstan, Summer 2022.

Travel in Kyrgyzstan, Kazakhstan, Uzbekistan, Azerbaijan, Georgia, Armenia.

\section{References}

\begin{tabular}[t]{@{}p{0.47\textwidth}@{\hspace{0.06\textwidth}}p{0.47\textwidth}@{}}
  \begin{minipage}[t]{\linewidth}\raggedright
    Dr Jody LaPorte\\
    Gonticas Fellow in Politics and International Relations\\
    Lincoln College\\
    University of Oxford\\
    \url{jody.laporte@lincoln.ox.ac.uk}
  \end{minipage}
  &
  \begin{minipage}[t]{\linewidth}\raggedright
    Dr Katerina Tertytchnaya\\
    Associate Professor of Comparative Politics\\
    Department of Politics and International Relations\\
    University of Oxford\\
    \url{katerina.tertytchnaya@politics.ox.ac.uk}
  \end{minipage}
  \\[12pt]
  \begin{minipage}[t]{\linewidth}\raggedright
    Professor Lenka Buštíková\\
    Department of Political Science\\
    University of Florida\\
    \url{lenka.bustikova@ufl.edu}
  \end{minipage}
  &
\end{tabular}

\end{document}
